\documentclass[letterpaper,11pt]{article}

\usepackage{fontawesome}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcolumntype{y}[1]{>{\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}
\newcommand{\resumeExperience}[4]{
  \vspace{1pt}\item
    \begin{tabular}{y{185pt}y{165pt}y{181pt}}
      \textbf{#1} &
      \centering\textbf{#3} &
      \hspace*{\fill}\textit{#4} #2 \\
    \end{tabular}\vspace{-7pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://florianwoelki.com/}{\Large Florian Woelki}}
  \href{https://github.com/FlorianWoelki}{\faicon{github}}
  \href{https://www.linkedin.com/in/florian-woelki/}{\faicon{linkedin-square}}
  \href{https://www.youtube.com/channel/UC18qytfIhR9cNEjUcgGLl3A}{\faicon{youtube-play}}
  & Email : \href{mailto:florianwoelki@gmx.de}{florianwoelki@gmx.de}\\
  \href{https://florianwoelki.com/}{https://www.florianwoelki.com} & Mobile : +49 1515 8364185\\
\end{tabular*}


%--------PROGRAMMING SKILLS------------
\section{Skills}
  TypeScript \textbar{} JavaScript \textbar{} Go \textbar{} Python \textbar{} SQL \textbar{}
  NoSQL \textbar{} Node \textbar{} React \textbar{} Vue \textbar{} PyTorch \textbar{}
  Machine Learning \textbar{} AWS \textbar{} Docker \textbar{} Kubernetes \textbar{}
  CI/CD \textbar{} Unit Testing \textbar{} E2E Testing \textbar{}
  English, German - \textit{All professional proficiency or above}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeExperience
      {Software Engineer II}{2023 - today}
      {Trade Republic}{Berlin, Germany}
      \resumeItemListStart
        \item
          {Coming Soon}
          \vspace{-3.5pt}
      \resumeItemListEnd

    \resumeExperience
      {Web Team Lead}{2022 - 2023}
      {Complori / Codary}{Berlin, Germany}
      \resumeItemListStart
        \item
          {Led the web team of 5 people building a more scalable and maintainable web architecture using technologies like \textbf{Google Cloud}, \textbf{React}, and \textbf{Next}, resulting in a decrease of the bundle size by over 30\%.}
          \vspace{-3.5pt}
        \item
          {Led the development of a scalable interactive web coding IDE using \textbf{Go}, \textbf{React}, \textbf{Next}, and \textbf{Google Cloud} resulting in an overall increase of customer retention and satisfaction.}
          \vspace{-3.5pt}
        \item
          {Achieved with the founders to get an investment of a seven-figure sum to develop an application in the field of education and machine learning.}
          \vspace{-3.5pt}
        \item
          {Continuous Integration/Deployment pipeline integration, load/stress testing, unit/integration/e2e testing leading to a more stable and reliable web application.}
          \vspace{-3.5pt}
        \item
          {Provided mentorships to team members and interns through 1-1 meetings and code reviews.}
          \vspace{-3.5pt}
      \resumeItemListEnd
      
    \resumeExperience
      {IT Consultant}{2019 - 2021}
      {Company Consulting Team}{Berlin, Germany}
      \resumeItemListStart
        \item
          {Engineering owner of an inhouse HR and polling tool that increased the productivity of other teams and the interactivity in meetings using \textbf{Vue}, \textbf{TypeScript}, and \textbf{Node}.}
          \vspace{-3.5pt}
        \item
          {Designed and developed a highly effective landing page with \textbf{React} and \textbf{TypeScript} for a real estate company, resulting in a 30\% increase in leads.}
          \vspace{-3.5pt}
        \item
          {Utilizing \textbf{Python} and \textbf{SQL} to merge and analyze multiple data sources for a data science project, resulting in valuable insights and actionable recommendations for the client.}
      \resumeItemListEnd

    \resumeExperience
      {Fullstack Softwarearchitect}{2017 - 2022}
      {Deutsche Telekom}{Berlin, Germany}
      \resumeItemListStart
        \item
          {Designed and developed a frontend and backend microservice architecture with \textbf{TypeScript}, \textbf{Java}, \textbf{Hibernate}, \textbf{Vue}, \textbf{React}, and \textbf{SQL} for a client's migration from a monolith application.}
          \vspace{-3.5pt}
        \item
          {Built a real-time situational awareness dashboard with efficient event and KPI calculation using \textbf{Java}, \textbf{SpringBoot}, \textbf{Scala}, \textbf{React}, and \textbf{TypeScript}, to improve decision-making in critical situations.}
          \vspace{-3.5pt}
        \item
          {Build and compared different machine and deep learning algorithms for a BLE proximity solution with variable object configuration in indoor areas resulting in a decrease of costs and increase in accuracy developed in \textbf{Python}, \textbf{Tensorflow}, and \textbf{Kotlin}.}
          \vspace{-3.5pt}
        \item
          {Spearheaded the full-stack development with \textbf{Java}, \textbf{SpringBoot}, \textbf{Scala}, and \textbf{React} of a real-time indoor asset tracking service, leveraging cutting-edge technologies such as UWB, LTE, and BLE.}
          \vspace{-3.5pt}
        \item
          {Designed and developed an android app with \textbf{Kotlin} and \textbf{SQL} that pairs a Bluetooth Low Energy Beacon with a QR-Code which had a significant contribution to the overall team productivity.}
          \vspace{-3.5pt}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Science in Artificial Intelligence}{Remote, Germany}
      {IU International University / London South Bank University}{2021 - 2024}
      \vspace{-10pt}
    \resumeSubheading
      {Bachelor of Science in Computer Science}{Leipzig, Germany}
      {Dual Study on HfTL and Deutsche Telekom}{2017 - 2020}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Highlighted personal Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/FlorianWoelki/reflow}{reflow}}
      {Compiled and interpreted programming language that is easy to learn and easy to use developed in Go.}
      \vspace{-5pt}
    \resumeSubItem{\href{https://github.com/FlorianWoelki/kira}{kira}}
      {Scalable and production ready remote code execution engine that allows to run code in an isolated environment developed with Go including a web code editor written in React.}
      \vspace{-5pt}
    \resumeSubItem{\href{https://sketchy-virid.vercel.app/}{sketchy}}
      {Rendering and animating handwritten-like SVG with a custom rendering engine.}
      \vspace{-5pt}
    \resumeSubItem{\href{https://github.com/FlorianWoelki/obsidian-icon-folder}{Icon Folder}}
      {Plugin for the obsidian editor to add icons of any kind to your folders/files which has over 200000 downloads.}
      \vspace{-5pt}
    % \resumeSubItem{\href{https://github.com/FlorianWoelki/todover}{todover}}
    %   {Weekly planer web application for easier managing your tasks and deadlines made with Vue, TypeScript, Node, Postgres, Prisma, and GraphQL.}
    %   \vspace{-5pt}
    % \resumeSubItem{\href{https://github.com/FlorianWoelki/rnn}{rnn}}
    %   {Highly efficient and minimalistic deep learning library developed in rust.}
    %   \vspace{-5pt}
    % \resumeSubItem{\href{https://github.com/FlorianWoelki/insta-clone}{insta-clone}}
    %   {Scalable instagram clone powered by microservices, React, TypeScript, Go, and gRPC.}
    %   \vspace{-5pt}
  \resumeSubHeadingListEnd


% %--------OTHERS------------
% \section{Others}
%   \resumeSubHeadingListStart
%     \resumeSubItem{STARTHACK Hackathon}
%       {Won the first price on a challenge for developing an interactive map where residents of Switzerland could post infrastructure improvements and vote on them.}
%       % \vspace{-5pt}
%     % \resumeSubItem{\href{https://florianwoelki-dlr-slides.vercel.app/}{Talk: Applications of GPT-3}}
%     %   {Invited by DLR to give a keynote presentation regarding the applications in software development of the language model GPT-3.}
%     %   \vspace{-5pt}
%     % \resumeSubItem{\href{https://youtu.be/m9kapfxwYOA}{Talk: What is artificial intelligence?}}
%     %   {Twenty minute talk about what artificial intelligence is and is not.}
%   \resumeSubHeadingListEnd
\end{document}
